Galois Transformers and Modular Abstract Interpreters

### 2014-11-13 writeup/pldi15.tex
edits
Balance bib.
hangers

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{stmaryrd}
\usepackage{galois}
\usepackage{float}
\usepackage{latexsym}
\floatstyle{boxed}
\restylefloat{figure}

@@

%\title{The Marriage of Monad Transformers and Abstract Interpreters: Modular Metatheory for Program Analysis}
\title{Galois Transformers and Modular Abstract Interpreters:\\ Reusable Metatheory for Program Analysis}
\authorinfo{David Darais}{Harvard University, USA}{darais@seas.harvard.edu}
\authorinfo{Matthew Might}{University of Utah, USA}{might@cs.utah.edu}
\authorinfo{David Van Horn}{University of Maryland, USA}{dvanhorn@cs.umd.edu}
\maketitle

@@

The design and implementation of static analyzers have becoming increasingly
systematic.  In fact, for large classes of analyzers, design and implementation
have remained seemingly (and now stubbornly) on the verge of full mechanization
for several years.  A stumbling block in full mechanization has been the
\emph{ad hoc} nature of soundness proofs accompanying each analyzer. While
design and implementation is largely systematic, soundness proofs can change
significantly with what seem like minor changes to the semantics and analyzers
themselves.  An achievement of this work is to systematize, parameterize and
modularize the proofs of soundness, so as to make them composable across
analytic properties.

@@

We solve the problem of systematically constructing static analyzers by
introducing the notion of a \emph{Galois transformer}, a monad transformer that
transports Galois connection properties.  In concert with a monadic
interpreter, we are able to define a library of monad transformers that
implement and represent classic context-, path-, and heap-(in-)sensitive
building blocks.  Moreover, these can be composed together to realize a program
analysis monad, \emph{independent of the language being analyzed}.

@@

\bibliographystyle{abbrvnat}
\bibliography{dvanhorn,davdar}

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{stmaryrd}
\usepackage{galois}
\usepackage{float}
\usepackage{latexsym}
\usepackage{balance}
\floatstyle{boxed}
\restylefloat{figure}
\usepackage[font=small,skip=0pt]{caption}

@@

%\title{The Marriage of Monad Transformers and Abstract Interpreters: Modular Metatheory for Program Analysis}
\title{Galois Transformers and Modular Abstract Interpreters}
\subtitle{Reusable Metatheory for Program Analysis}
\authorinfo{David Darais}{Harvard University, USA}{darais@seas.harvard.edu}
\authorinfo{Matthew Might}{University of Utah, USA}{might@cs.utah.edu}
\authorinfo{David Van Horn}{University of Maryland, USA}{dvanhorn@cs.umd.edu}
\maketitle

@@

The design and implementation of static analyzers have becoming increasingly
systematic.  In fact, for large classes of analyzers, design and implementation
have remained seemingly (and now stubbornly) on the verge of full mechanization
for several years.  A stumbling block in full mechanization has been the
\emph{ad hoc} nature of soundness proofs accompanying each analyzer. While
design and implementation is largely systematic, soundness proofs can change
significantly with seemingly minor changes to the semantics or analyzers.  An
achievement of this work is to systematize, parameterize and modularize the
proofs of soundness, so as to make them composable across analytic properties.

@@

We solve the problem of systematically constructing static analyzers by
introducing \emph{Galois transformers}: monad transformers that
transports Galois connection properties.  In concert with a monadic
interpreter, we define a library of monad transformers that
implement building blocks for classic analysis parameters like context-, path-,
and heap-(in-)sensitivity. Moreover, these can be composed together 
% to realize a program analysis monad, 
\emph{independent of the language being analyzed}.

@@

\balance
\bibliographystyle{abbrvnat}
\bibliography{dvanhorn,davdar}
